### 2024-06-21 manuscript.Rmd
reinstate backtics in title
typo

---
title             : "reprodubileRchunks: R Markdown Code Chunks with Automated Reproducibility Tests"
shorttitle        : "Title"
author: 
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
    corresponding : no    # Define only one corresponding author
    address       : "Rüdesheimer Str. 50, 14197 Berlin"
    email         : "andreas.brandmaier@medicalschool-berlin.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

@@

abstract: |
 Computational results are considered _reproducible_ if the same computation on the same data yields the same results if performed on a different computer or on the same computer later in time. Reproducibility is a prerequisite for replicable, robust and transparent research in digital environments.
 Various approaches have been suggested to increase chances of reproducibility.
 Many of them rely on R Markdown as a language to dynamically generate reproducible research assets (e.g., reports, posters, presentation).
 However, a simple way detect changes of these assets, i.e. irreproducibility, is still missing.
 We introduce the R package `reproducibleRchunks`, which provides a new type of code chunk in R Markdown documents, which automatically store meta data about original computational results and check later reproductions of the research assets for reproduction. 
 With a minimal change to users' workflows, we hope that this approach increases transparency and trustworthiness of research assets.

>>>>

---
title             : "`reprodubileRchunks`: R Markdown Code Chunks with Automated Reproducibility Tests"
shorttitle        : "Title"
author: 
  - name          : "Andreas M. Brandmaier"
    affiliation   : "1,2,3"
    corresponding : no    # Define only one corresponding author
    address       : "Rüdesheimer Str. 50, 14197 Berlin"
    email         : "andreas.brandmaier@medicalschool-berlin.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

@@

abstract: |
 Computational results are considered _reproducible_ if the same computation on the same data yields the same results if performed on a different computer or on the same computer later in time. Reproducibility is a prerequisite for replicable, robust and transparent research in digital environments.
 Various approaches have been suggested to increase chances of reproducibility.
 Many of them rely on R Markdown as a language to dynamically generate reproducible research assets (e.g., reports, posters, presentation).
 However, a simple way to detect changes of these assets, i.e. irreproducibility, is still missing.
 We introduce the R package `reproducibleRchunks`, which provides a new type of code chunk in R Markdown documents, which automatically store meta data about original computational results and check later reproductions of the research assets for reproduction. 
 With a minimal change to users' workflows, we hope that this approach increases transparency and trustworthiness of research assets.
